---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE,fig.align='center',message = F)
knitr::read_chunk("CountriesSummary.R")


```

```{r dataSection, echo=FALSE}
```

# {.tabset }

##English

<br>

<p align="center" style="font-size:21pt; font-family:Calibri">
A Scoreboard Throughout Time
</p>

<br>
<br>

<p align="left" style="font-size:17pt; font-family:Calibri">

□	A Summary of Each Country’s Rank and Status in TIMSS and PIRLS 2015
</p>

</p>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
In this section, using maps, we have shown the participant countries' statistics for PIRLS as well as TIMSS 4th and 8th grade in the year 2015. 
</p>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Moving the cursor to each region, you can view information about that region such as total number of participants, female/male number of participansts, average score in Mathematics, etc. 
</p>
 
 <br>
 
```{r timss8th}
```

 <br>
 


```{r timss4th}
```

 <br>
 <br>
 
 

```{r }
<<pirls>>
```


<br>
<br>
 
 


<p align="left" style="font-size:17pt; font-family:Calibri">

□	An Overview of Countries' Performances Throughout Time in TIMSS 
</p>

<br>
 

```{r }
<<timssMotion>>
```

<br>
<br>

##Farsi

<br>
<br>

<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□ خلاصه وضعیت کشور ها در دو آزمون Timss و Pirls در سال 2015 :
</p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در این قسمت با استفاده از نقشه، وضعیت کشورهای شرکت کننده برای PIRLS و همچنین سال چهارم و هشتم TIMSS برای سال ۲۰۱۵  را نشان داده ایم. </p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">

با بردن اشاره گر روی هر کشور اطلاعاتی از قبیل تعداد کل شرکت کننده ها، تعداد شرکت کننده های دختر، تعداد شرکت کننده های پسر، میانگین امتیاز در ریاضی و ...  نیز قابل مشاهده است.
 </p>
 
 <br>
 
```{r timss8th}
```


 <br>
 


```{r timss4th}
```

 <br>
 <br>
 
 

```{r pirls}

```


<br>
<br>
 
 


<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□ مشاهده وضعیت کلی کشور ها در طول سال ها در آزمون Timss :
</p>

<br>
 

```{r timssMotion}

```

<br>
<br>

