---
title: ""
output: html_document
---


```{r setup, include=FALSE, cache = F}

knitr::opts_chunk$set(warning = FALSE, fig.align='center',fig.width=12,fig.height=8,message = F, error = T)
knitr::read_chunk("FactorAnalysis.R")

```

```{r dataSection,echo=FALSE}
```

# {.tabset }

##English

<br>

<p align="center" style="font-size:21pt; font-family:Calibri">
Grouping Countries Based on Students’ Opinion on Mathematics
</p>


<br>

<p align="left" style="font-size:19pt; font-family:Calibri">
□	Gathering The Data
</p>

<br> <br>

<p align="left" style="font-size:17pt; font-family:Calibri">
□□	Based on Interest
</p>

<br> <br> <br>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
We have considered the answers to these questions (questiones are writen directly from the questionnaire)
</p>

<br>

<ul style="list-style-type:circle; font-size:15pt; font-family:Calibri" align="left">
  <li>I enjoy learning mathematics</li>
  <li>I wish I did not have to
study mathematics</li>
  <li>Mathematics is boring </li>
  <li>I learn many interesting
things in mathematics</li>
  <li>I like mathematics</li>
  <li>I like any schoolwork that
involves numbers</li>
  <li>I like to solve
mathematics problems</li>
  <li>I look forward to
mathematics class</li>
  <li>Mathematics is one of
my favorite subjects</li>
</ul> 

<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Students gave a score ranging from 1 to 5 to each question, 1 meaning Disagree a lot, 5 meaning Agree a lot. Afterwards we calculated the average score for each individual country to the questions. For example, you can view the gathered data for 3 selected countries in this table:
</p>

<br> <br> 
```{r , echo = F}
<<table>>
```

<br> <br> <br>


<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
We performed the k-means algorithm on this data. The result of this algorithm can be seen in the biplot shown below:
</p>


<br> <br> <br>
```{r , echo = F}
<<biplot1>>
```
<br> <br> <br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
The correlation of the answers to each question with the top 5 principal components were as such:
</p>


<br> <br> <br>

```{r , echo = F}
<<corHC1>>
```

<br> <br>
<hr> <hr>
<br>


<p align="left" style="font-size:17pt; font-family:Calibri">
□□	Based on Talent
</p>

<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
In this section and the one after, we have taken the same steps and the previous one. Therefor we refrain from repeting the descriptions. 
</p>

<br>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
We have considered the answers to these questions (questiones are writen directly from the questionnaire)
</p>

<br>

<ul style="list-style-type:circle; font-size:15pt; font-family:Calibri" align="left">
  <li>I usually do well in mathematics</li>
  <li>Mathematics is more difficult
for me than for many of
my classmates</li>
  <li>Mathematics is not one of
my strengths</li>
  <li>I learn things quickly
in mathematics</li>
  <li>Mathematics makes me
nervous</li>
  <li>I am good at working out
difficult mathematics problems</li>
  <li>My teacher tells me I am good at mathematics </li>
  <li>Mathematics is harder for me
than any other subject</li>
  <li>Mathematics makes me
confused</li>
</ul> 


<br>


<br> <br> <br>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
biplot
</p>
<br> <br> <br>
```{r , echo = F}
<<biplot2>>
```
<br> <br> <br>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Correlation Matrix
</p>
<br> <br> <br>

```{r , echo = F}
<<corHC2>>
```

<br> <br>
<hr> <hr>
<br>


<p align="left" style="font-size:17pt; font-family:Calibri">
□□	Based on significance
</p>

<br>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
We have considered the answers to these questions (questiones are writen directly from the questionnaire)
</p>

<br>

<ul style="list-style-type:circle; font-size:15pt; font-family:Calibri" align="left">
  <li>I think learning mathematics will help me in my daily life</li>
  <li>I need mathematics to learn other school subjects</li>
  <li>I need to do well in mathematics
to get into the <university> of
my choice</li>
  <li>I need to do well in mathematics
to get the job I want</li>
  <li>I would like a job that involves
using mathematics</li>
  <li>It is important to learn about mathematics to get ahead in the world</li>
  <li>Learning mathematics will
give me more job opportunities
when I am an adult</li>
  <li>My parents think that it is
important that I do well in mathematics </li>
  <li>It is important to do well in mathematics</li>
</ul> 

<br>


<br>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
biplot
</p>
<br> <br> <br>
```{r , echo = F}
<<biplot3>>
```
<br> <br> <br>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Correlation Matrix
</p>
<br> <br> <br>

```{r , echo = F}
<<corHC3>>
```



<br> <br>
<hr> <hr>
<br>

<p align="left" style="font-size:19pt; font-family:Calibri">
□	Performing Factor Analysis
</p>

<br> 
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
In this section we have used the `psych` and `GPArotation` packages. 
</p>

<br> <br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
first we concatenate all the data used for the previous steps. Afterwards, using the `fa.parallel()` function we obtain the number of factors we need. 
</p>

<br> 
```{r , echo=FALSE}
<<data>>
```

```{r , echo = F, message = T}
<<FA>>
```
<br> <br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
According to the chart, 3 factors seem sufficient. 
</p>

<br> <br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Next we much select a rotation model. For this data, we have selected the oblique model since based on the correlation matrices and the PCA charts displayed in the previous sections, it is clear that a few of the variables are correlated. 
</p>

<br> <br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Also, based on the instructions given in R's documentation:
</p>


> <p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
<i>
fm = "minchi" will minimize the sample size weighted chi square when treating pairwise correlations with different number of subjects per pair.
</i>
</p>

 <br> <br>
<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Finally, we run the algorithm. 
</p>

<br> <br>
```{r , echo = F}
<<FA2>>
```



<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Here, you can view a diagram of the factors.  
</p>

<br> <br>

```{r, echo = F}
 fa.diagram(country.fa)
```

<br> <br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Here, you can view a diagram of the factors.  
</p>

<br> <br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
At last, below you can see the result of the algorithm. 
</p>


<br> <br>
```{r, echo = F}
 country.fa
```



<br> <br> <br>

##Farsi
<p dir="RTL" align="right" style="font-size:21pt; font-family:B Nazanin">
• دسته بندی کشورها براساس نظراتشان در رابطه با ریاضی
</p>

<br>
<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□ جمع آوری داده
</p>

<br> <br>

<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□□ بر حسب علاقه
</p>

<br> <br> <br>
<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
سوالات زیر را انتخاب کردیم:
</p>

<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
  <ul style="list-style-type:circle; font-size:15pt; font-family:B Nazanin" dir="RTL" align="right">
  <li>از یاد گرفتن ریاضیات لذت میبرم.</li>
  <li>آرزو میکنم کاش لازم نبود ریاضی یاد بگیرم</li>
  <li>ریاضی کسل کننده است</li>
  <li>من خیلی مسائل جالبی در ریاضی یاد میگیرم</li>
  <li>من ریاضی را دوست دارم</li>
  <li>من هرگونه مشق مرتبط با ریاضی را دوست دارم</li>
  <li>من حل مسائل ریاضی را دوست دارم</li>
  <li>من چشم انتظار کلاس های ریاضیم هستم</li>
  <li>ریاضی یکی از موضوعات موردعلاقه من است</li>
  </ul> 
</p>

<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
به هر سوال از ۱ تا ۴ امتیاز داده اند. ۱ به معنای کاملا مخالف و ۵ به معنای کاملا موافق است. سپس در هر سوال میانگین امتیاز دانش آموزان برای هر کشور را بدست آوردیم. برای مثال بدین صورت:
</p>

<br> <br> 
```{r table, echo = F}

```

<br> <br> <br>


<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
سپس روی این داده الگوریتم k-means را اجرا کردیم. نتیجه ی این الگوریتم را بر روی نمودار biplot زیر مشاهده میفرمایید. 
</p>

<br> <br> <br>
```{r biplot1, echo = F}

```

<br> <br> <br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
همچنین کورلیشن متغیرها را با مولفه های اصلی به دست آورده ایم:
</p>

<br> <br> <br>

```{r corHC1, echo = F}
```

<br> <br>
<hr> <hr>
<br>


<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□□ بر حسب استعداد
</p>

<br>
<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در این قسمت و همچنین قسمت بعد، همانند قسمت قبلی عمل کرده ایم، پس از توضیحات اضافی پرهیز میکنیم.
</p>

<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در این قسمت سوالات زیر را بررسی کرده ایم:
</p>

<br>


<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
  <ul style="list-style-type:circle; font-size:15pt; font-family:B Nazanin" dir="RTL" align="right">
  <li>من معمولا در ریاضی خوب عمل میکنم</li>
  <li>ریاضی برای من نسبت به بقیه ی همکلاسی هایم سخت تر است</li>
  <li>ریاضی از نقات قوت من نیست </li>
  <li>من سریع مسائل را در ریاضی یاد میگیرم</li>
  <li>ریاضی باعث استرس من میشود</li>
  <li>من در حل مسائل دشوار ریاضی قوی عمل میکنم</li>
  <li>معلمم به من میگوید که من در ریاضی قوی هستم</li>
  <li>ریاضی برای من سخت تر از درس های دیگر است</li>
  <li>ریاضی باعث می شود من گیج بشوم</li>
  </ul> 
</p>

<br>


<br> <br> <br>
<p dir="RTL" align="right" style="font-size:17pt; font-family:B Nazanin; text-indent:30px">
نمودار biplot
</p>
<br> <br> <br>
```{r biplot2, echo = F}

```
<br> <br> <br>
<p dir="RTL" align="right" style="font-size:17pt; font-family:B Nazanin; text-indent:30px">
ماتریس کورلیشن ها
</p>
<br> <br> <br>

```{r corHC2, echo = F}
```


<br> <br>
<hr> <hr>
<br>


<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□□ بر حسب اهمیت
</p>

<br>
<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در این قسمت سوالات زیر را بررسی کردیم:
</p>


<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
  <ul style="list-style-type:circle; font-size:15pt; font-family:B Nazanin" dir="RTL" align="right">
  <li>من فکر میکنم یادگیری ریاضی در زندگی روزمره به من کمک خواهد کرد</li>
  <li>من به ریاضی نیاز دارم تا درس های دیگر را یاد بگیرم</li>
  <li>من به ریاضی نیاز دارم تا بتوانم در دانشگاه مورد علاقه ام قبول شوم</li>
  <li>من به ریاضی نیاز دارم تا بتوانم به شغل مورد علاقه ام برسم</li>
  <li>من دوست دارم شغلی مرتبط با ریاضی داشته باشم</li>
  <li>یادگیری ریاضی برای پیشرفت در دنیا مهم است</li>
  <li>یادگیری ریاضی وقتی بزرگ بشوم برای من موقعیت های شغلی زیادی ایجاد خواهد کرد</li>
  <li>والدینم فکر میکنند که مهم است که من در ریاضی خوب عمل کنم</li>
  <li>قوی عمل کردن در ریاضی اهمیت دارد</li>
  </ul> 
</p>

<br>


<br>
<p dir="RTL" align="right" style="font-size:17pt; font-family:B Nazanin; text-indent:30px">
نمودار biplot
</p>
<br> <br> <br>
```{r biplot3, echo = F}

```
<br> <br> <br>
<p dir="RTL" align="right" style="font-size:17pt; font-family:B Nazanin; text-indent:30px">
ماتریس کورلیشن ها
</p>
<br> <br> <br>

```{r corHC3, echo = F}
```


<br> <br>
<hr> <hr>
<br>

<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□ پیاده سازی factor analysis بر روی داده
</p>

<br> 
<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در این مرحله از پکیج های `psych` و `GPArotation` استفاده خواهیم کرد
</p>

<br> <br>


<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
ابتدا همه ی داده های سری قبل را به هم میچسبانیم.  سپس با استفاده از تابع `fa.parallel()` بررسی میکنیم که چه تعداد فاکتور لازم است:
</p>

<br> 
```{r data, echo=FALSE}
```

```{r FA, echo = F, message = T}

```
<br> <br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
با توجه به نتایج تابع میفهمیم ۳ فاکتور کافی است. 
</p>

<br> <br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
حال باید مدل rotation را انتخاب کنیم. برای این داده ها مدل oblique را انتخاب کرده ایم زیرا با توجه به ماتریس های کورلیشن و نمودارهای PCA که در قسمت های قبل کشیدیم، واضح است که بین یک سری از متغیرها کورلیشن موجود است.
</p>

<br> <br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
همچنین بر حسب توضیحات r :
</p>

> <p dir="LTR" align="left" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
fm = "minchi" will minimize the sample size weighted chi square when treating pairwise correlations with different number of subjects per pair.
</p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
مدل فاکتور کردن را از نوع minchi انتخاب کرده ایم.
</p>
 <br> <br>
<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
حال الگوریتم را اجرا میکنیم.
</p>

<br> <br>
```{r FA2, echo = F}

```



<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
دیاگرام فاکتور ها را رسم میکنیم:
</p>

<br> <br>

```{r, echo = F}
fa.diagram(country.fa)
```

<br> <br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
فاکتور ها به نظر میرسد که درست تعیین شده اند. 
</p>

<br> <br>
<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در نهایت نتیجه ی الگوریتم را نمایش میدهیم:
</p>
<br> <br>
```{r, echo = F}
country.fa
```



<br> <br> <br>

