---
title: ""
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, fig.align='center',fig.width=17,fig.height=12,message = F)

knitr::read_chunk("GOOD_READER_GOOD_COUNTRIES.R")

```

```{r dataSection, echo=FALSE}
```

# {.tabset }

##English

<br> <br>

<p align="center" style="font-size:21pt; font-family:Calibri">
What Makes a Good Reader
</p>

<br>

<p align="left" style="font-size:17pt; font-family:Calibri">
□ Successful Countries’ Performance in PIRLS 2015
</p>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Students from Singapore and Russia had the best performance in PIRLS 2015. In these two countries, more than 25% of the participants were Advanced based on PIRLS benchmarks. 
</p>
<br>
```{r }
<<top2>>
```

<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Hong Kong, Ireland and Poland ranked 3rd, 4th and 5th respectively. 
<br> 
20% percent of participants had reached the Advanced benchmark in these three countries. 
</p>
<br>

```{r }
<<top5>>

```
<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Only 1% of Iran's population reached the advanced benchmark.
</p>
<br>

```{r }
<<iran>>

```

<br>

<p align="left" style="font-size:17pt; font-family:Calibri">
□ The Concept of A "Good Reader" in PIRLS 
</p>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
In this section, we study participants known as <i>Good Readers</i> in the PIRLS exam. In the previous sections we focused on factors contributing to students' performance, and here we focus more on visualizations. 
<br> 
Having parents who engage students from childhood in literary activities and also attending pre-primary school, is one of these <i>Good Readers</i>' traits. 
</p>
<br>

```{r }
<<earlyStart>>
```

<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Attending richer schools with more facilities, is also one of their traits.
</p>

```{r }
<<wellResourced>>
```

<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
These group of students attend safer and more disciplined schools. 
</p>

<br>

```{r }
<<safe>>
```


##Farsi

<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□ عملکرد کشور های موفق در آزمون Pirls 2015 :
</p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
دانش آموزان دو کشور روسیه و سنگاپور بهترین عملکرد را در آزمون Pirls 2015 داشته اند.
<br>
در این دو کشور بیشتر از 25 درصد دانش آموزان به معیار Advanced این آزمون رسیده اند.
</p>
<br>

```{r top2}

```
<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در رده های بعدی 3 کشور هنگ کنگ ، ایرلند و لهستان قرار دارند.
<br>
در این 3 کشور یک پنجم از دانش آموزان به معیار Advanced این آزمون رسیده اند.
</p>
<br>

```{r top5}


```
<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
وضعیت ایران در این آزمون.
در ایران فقط 1 درصد از دانش آموزان به معیار Advanced آزمون رسیدند.
</p>
<br>

```{r iran}


```

<br>

<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□ مفهوم “خواننده خوب” در آزمون Pirls :
</p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در این بخش به بررسی افرادی که در آزمون Pirls به عنوان "خواننده خوب" شناخته می شوند می پردازیم.
<br>
در قسمت های قبل به عوامل موثر در عملکرد پرداخته ایم و اینجا به تصویر پردازی بیشتر می پردازیم.
</p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
داشتن والدینی که از کودکی فرزند را مشفول به کار های ادبی کند و همینطور رفتن به پیش دبستانی یمی از ویژگی های این افراد است.
</p>
<br>

```{r earlyStart}

```
<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
رفتن به مدارسی با امکانات بیشتر و دانش آموزانی با سطح اقتصادی بالاتر نیز یکی از ویژگی های آن ها می باشد.
</p>
<br>

```{r wellResourced}

```
<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
این گروه از دانش آموزان در مدسه هایی با امنیت و نظم بیشتر می روند.
</p>
<br>

```{r safe}

```

