---
title: ""
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,warning = FALSE, fig.align='center',fig.width=17,fig.height=12,message = F)

knitr::read_chunk("IranSingapore.R")
```

```{r dataSection, echo=FALSE}
```

# {.tabset }

##English

<p align="center" style="font-size:21pt; font-family:Calibri">
 Comparing Iran to Singapore, The #1 Country in TIMSS
</p>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
In this section, we focus on comparing Iran and Singapore in different areas.
<br> 
First we try to compare the two countries based on economic and education indicators. 
<br>
Below we have included the charts for each indicator. The time period chosen was between 2011 and 2014 (4 years time difference between the last two TIMSS exams.)
</p>
<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
The chosen indicators were Government Expenditure on Education, Literacy Rate among youths, Percentage of Urban Population, Population Density, Life Expectency, etc.  
</p>

<br>

```{r }
<<lr>>
```

<br>

```{r }
<<le>>
```

<br>

```{r }
<<urbanPop>>
```

<br>

```{r }
<<population>>
```

<br>


```{r }
<<educationExpenditure>>
```

<br>

```{r }
<<popDensity>>
```

<br>

```{r }
<<infantMR>>
```


<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
As you can see, Singapore is better in these areas.  
</p>

<br>

<p align="left" style="font-size:17pt; font-family:Calibri">
□	Comparing Performance in Mathematics And Science
</p>


<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Now we would like to compare the average score of these two countries in each domain. 
</p>


```{r }
<<iranvsSingapore>>
```


<br>


```{r }
<<iranvsSingapore2>>

```

<br>


```{r }
<<iranvsSingapore3>>
```

<br>


```{r }
<<iranvsSingapore4>>
```

<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Singapore has a better performance by far. 
</p>

<p align="left" style="font-size:17pt; font-family:Calibri">
□	Differences in Average Score From 2003 to 2015
</p>

<br>

```{r }
<<avgChange>>
```


<br>

```{r }
<<avgChange2>>
```

<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Both countries have improved, but still Iran's performance is much lower. 
</p>

<br>

<p align="left" style="font-size:17pt; font-family:Calibri">
□	Score Range
</p>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
In this last section, we have drawn the score range for these two countries in both grades and subject. 
</p>

```{r }
<<rangeScores>>
```

<br>

```{r }
<<rangeScores2>>
```

<br>
<br>

<p align="left" style="font-size:15pt; font-family:Calibri;  text-indent:30px">
Iran's lower bound is way lower than Singapore, but it's upper bound is somewhat closer. 
</p>

<br>
<br>
<br>

##Farsi

<p dir="RTL" align="right" style="font-size:19pt; font-family:B Nazanin">
□ مقایسه ایران و سنگاپور
</p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
در این بخش می خواهیم به مقایسه ایران و سنگاپور از جنبه های مختلف بپردازیم.
<br>
در ابتدا سعی به مقایسه دو کشور بر اساس شاخص های اقتصادی و تحصیلی می کنیم.
<br>
در زیر نمودار های هر یک از شاخص ها آمده است. بازه زمانی انتخاب شده بین 2011 تا 2014 (4 سال زمان بین دو آزمون آخر تیمز) می باشد.
</p>

<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
شاخص های انتخاب شده شامل :  هزینه برای تحصیلات توسط دولت ، میزان سوار بین جوانان ، درصد جمعیت شعر نشین ، چگالی جمعیت ، امید زندگی و ... می باشد.
</p>

<br>

```{r lr}
```

<br>

```{r le}
```

<br>

```{r urbanPop}

```

<br>

```{r population}
```

<br>

```{r educationExpenditure}
```

<br>

```{r popDensity}
```

<br>

```{r infantMR}
```


<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
همانطور که مشاهده می کنیم سنگاپور وضعیت بهتری از این لحاظ دارد.
</p>

<br>


<p dir="RTL" align="right" style="font-size:18pt; font-family:B Nazanin; text-indent:30px">
مقایسه عملکرد در علوم و ریاضی در دو پایه :
</p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
حال می خواهیم میانگین نمره هر کشور را در هر یک از زیر گروه ها مقایسه کنیم.
</p>


```{r iranvsSingapore}
```

<br>


```{r iranvsSingapore2}

```

<br>


```{r iranvsSingapore3}

```

<br>


```{r iranvsSingapore4}
```

<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
سنگاپور با اختلاف دارای عملکرد بهتری می باشد.
</p>



<p dir="RTL" align="right" style="font-size:18pt; font-family:B Nazanin; text-indent:30px">
تغییرات میانگین در طی 3 دوره آزمون ها بین سال های 2003 تا 2015 :
</p>

<br>

```{r avgChange}
```


<br>

```{r avgChange2}
```

<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
هر دو کشور در طی این سال ها پیشرفت داشتند ولی هنوز عملکرد ایران بسیار پایین تر می باشد.
</p>

<br>

<p dir="RTL" align="right" style="font-size:18pt; font-family:B Nazanin; text-indent:30px">
بازه نمرات دو کشور :
</p>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
برای آخرین قسمت می خواهیم نمودار بازه نمرات دو کشور را در هر دو رشته و هر دو پایه رسم کنیم.
</p>

```{r rangeScores}
```

<br>

```{r rangeScores2}
```

<br>
<br>

<p dir="RTL" align="right" style="font-size:15pt; font-family:B Nazanin; text-indent:30px">
کف عملکرد ایران بسیار پایین تر از سنگاپور می باشد ولی عملکرد ماکسیمم ایران فاصله کمتری با ماکسیمم سنگاپور دارد.
</p>

<br>
<br>
<br>